Two-Phase Commit Using Blockchain

### 2022-06-04 paper/paper.tex
Fine tune.
Final edits.

\documentclass[11pt,sigplan,screen,nonacm]{acmart}
% \documentclass[11pt,conference]{IEEEtran}
% \IEEEoverridecommandlockouts
% \usepackage[sort,nocompress]{cite}
\usepackage{natbib}
\setcitestyle{square, comma, numbers,sort&compress, super}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage[toc,page]{appendix}
\usepackage{algorithmic}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{url}
\usepackage{xcolor}
\usepackage[htt]{hyphenat}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

% \author{\IEEEauthorblockN{Benjamin Marks}
  % \IEEEauthorblockA{\textit{Stanford University} \\
  % benmarks@stanford.edu}
  % \and
  % \IEEEauthorblockN{Heron Yang}
  % \IEEEauthorblockA{\textit{Stanford University} \\
  % heronyang@stanford.edu}
  % \and
  % \IEEEauthorblockN{Yuewei Na}
  % \IEEEauthorblockA{\textit{Stanford University} \\
  % yueweina@stanford.edu}
% }

@@

@@

% \begin{IEEEkeywords}
  % Atomic Commit, Blockchain, Smart Contract, Distributed System, Database Transaction.
% \end{IEEEkeywords}
\keywords{atomic commit, blockchain, smart contract, distributed system, database transaction}

@@

\subsubsection{Reliability}
Our system has better reliability than the traditional 2PC protocol for two reasons. First, the system leverages the blockchain to maintain the coordination state. The stateless coordinator can easily recover as long as it knows the participating cohorts. Second, The coordinator is stateless and horizontally scalable. We can keep multiple jobs running concurrently and place a load-balancing layer on top of it to be tolerant of individual coordinator node failures.

\section{Design Overview}
\subsection{Architecture and Components} \label{components}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{./diagram.pdf}
  \caption{This diagram displays the main components within our architecture and example steps of successfully committing a transaction.}
  \label{fig:Panel}
\end{figure*}

@@

\subsubsection{Database} \label{database}
The database component is responsible for committing sub-transactions in each cohort and abstracts typical ACID databases with 5 APIs in a \texttt{DatabaseAdapter:} 
\begin{itemize}
  \item \texttt{Begin()} starts a transaction.
  \item \texttt{Commit()} commits a started transaction.
  \item \texttt{Abort()} aborts a started transaction.
  \item \texttt{Put(key, value)} puts value in a row whose primary key is key.
  \item \texttt{Get(key)} gets the value from the row whose primary key is key.
\end{itemize}

@@

This section describes the end-to-end life of a transaction without handling failures.

\begin{enumerate}
  \item The client composes a transaction request and passes it to the coordinator through \texttt{CommitAomticTransaction()}. The coordinator returns a transaction ID for the client to look up the transaction result later.
  \item The coordinator asks the blockchain to trace votes for the new transaction through \texttt{Start-Voting()}.
  \item The coordinator decomposes the transaction into sub-transactions and distributes them to the corresponding cohort through \texttt{PrepareTransaction()}.
  \item Each cohort executes a sub-transaction by acquiring locks and forwarding the operations to the database up to the point before Commit(). The cohort writes an entry to the redo log to recover in case it crashes. Additionally, the cohort writes the \texttt{Get} operation results to disk for faster responses after a crash and recovery.
  \item The cohort votes to the blockchain through \texttt{Vote()} indicating that it wants to commit or abort the transaction.
  \item The cohort waits until the expected transaction vote timeout time and gets the voting decision from the blockchain through \texttt{GetVotingDecision()}.
  \item If the voting decision is to commit the transaction, the cohort commits the sub-transaction onto the database and releases any acquired locks; otherwise, it aborts the sub-transaction in the database and releases any acquired locks.
  \item (Independent of the previous steps) The client waits until the vote timeout time and requests the transaction result from the coordinator through \texttt{GetTransactionResult()}, using the transaction ID given in step 1.
  \item The coordinator gets (1) the voting decision of the inquiry transaction from the blockchain through \texttt{GetTransactionResult()} and (2) the \texttt{Get} operation results from each cohort.
\end{enumerate}

@@

\section{Implementation}
In this section we first describe the implementation of our overall system. Then, we illustrate the implementation of individual components. The source code of our implementation is available at licensed under GNU Lesser General Public License \cite{lgpl}. Our implementation depends on the following libraries: truffle \cite{github_truffle}, ganache \cite{github_ganache}, sqlite3 \cite{github_sqlite3}, grpc \cite{github_grpc}, web3 \cite{github_web3}, abseil-cpp \cite{github_absl}, rule\_nodejs \cite{github_rulejs}, gflags \cite{github_gflags}, glog \cite{github_glog}, openssl \cite{github_openssl}, threadpool \cite{Shoshany2021_ThreadPool}, lmdb \cite{github_lmdb}, and lmdbxx \cite{github_lmdbxx}.

@@

% \appendix
% \begin{table}[hbtp]
  % \centering
  % \caption{Gas used, cost in ETH/USD per blockchain transaction for a successful 2PC commit with 2 cohorts. Data as of 2022/05/30.}
  % \label{table:cost}
  % \begin{tabular}{|p{1.8cm}|p{1.8cm}|p{2cm}|p{1.8cm}|}
    % \hline
          % & Gas Used (Gwei) &  Cost in ETH & Cost in USD \\
          % \hline
    % StartVoting &73441 &0.000073441 & 0.143\\
    % \hline
    % Vote 1 &56451	&0.000056451 &0.110\\
    % \hline
    % Vote 2 &39513 &0.000039513 &0.077\\
    % \hline
    % Total &169405 &0.000169405 &0.330\\
    % \hline
  % \end{tabular}
% \label{blockchaingas}
% \end{table}

@@

  \begin{table}[hbtp]
    \centering
    \caption{Gas used, cost in ETH/USD per blockchain transaction for a successful 2PC commit with 2 cohorts. Data as of 2022/05/30.}
    \label{table:cost}
    \begin{tabular}{|p{1.8cm}|p{1.8cm}|p{2cm}|p{1.8cm}|}
      \hline
          & Gas Used (Gwei) &  Cost in ETH & Cost in USD \\
          \hline
      StartVoting &73441 &0.000073441 & 0.143\\
      \hline
      Vote 1 &56451	&0.000056451 &0.110\\
      \hline
      Vote 2 &39513 &0.000039513 &0.077\\
      \hline
      Total &169405 &0.000169405 &0.330\\
      \hline
    \end{tabular}
  \end{table}

>>>>

\documentclass[11pt,sigplan,screen,nonacm]{acmart}
\usepackage{natbib}
\setcitestyle{square, comma, numbers,sort&compress, super}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage[toc,page]{appendix}
\usepackage{algorithmic}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{url}
\usepackage{xcolor}
\usepackage[htt]{hyphenat}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

@@

\settopmatter{printfolios=true} % add page number

% hacky way to get some space below the author row.
\begin{teaserfigure}
\end{teaserfigure}

@@

\keywords{atomic commit, blockchain, smart contract, distributed system, database transaction}

@@

\subsubsection{Reliability}
Our system has better reliability than the traditional 2PC protocol for two reasons. First, the system leverages the blockchain to maintain the coordination state. The stateless coordinator can easily recover as long as it knows the participating cohorts. Second, the coordinator is stateless and horizontally scalable. We can keep multiple jobs running concurrently and place a load-balancing layer on top of it to be tolerant of individual coordinator node failures.

\section{Design Overview}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{./diagram.pdf}
  \caption{This diagram displays the main components within our architecture and example steps of successfully committing a transaction.}
  \label{fig:flow}
\end{figure*}

\subsection{Architecture and Components} \label{components}

@@

@@

\subsubsection{Database} \label{database}
The database component is responsible for committing sub-transactions in each cohort and abstracts typical ACID databases with five APIs in a \texttt{DatabaseAdapter:} 
\begin{itemize}
  \item \texttt{Begin()} starts a transaction.
  \item \texttt{Commit()} commits a started transaction.
  \item \texttt{Abort()} aborts a started transaction.
  \item \texttt{Put(key, value)} puts value in a row whose primary key is \texttt{key}.
  \item \texttt{Get(key)} gets the value from the row whose primary key is \texttt{key}.
\end{itemize}

@@

This section and Figure \ref{fig:flow} describe the end-to-end life of a transaction without failures.

\begin{enumerate}
  \item The client composes a transaction request and passes it to the coordinator through \texttt{CommitAomticTransaction()}. The coordinator returns a transaction ID for the client to look up the transaction result later.
  \item The coordinator asks the blockchain to trace votes for the new transaction through \texttt{Start-Voting()}.
  \item The coordinator decomposes the transaction into sub-transactions and distributes them to the corresponding cohort through \texttt{PrepareTransaction()}.
  \item Each cohort executes a sub-transaction by acquiring locks and forwarding the operations to the database up to the point before \texttt{Commit()}. The cohort writes an entry to the redo log to recover in case it crashes. Additionally, the cohort writes the \texttt{Get} operation results to disk for faster responses after a crash and recovery.
  \item The cohort votes to the blockchain through \texttt{Vote()} indicating that it wants to commit or abort the transaction.
  \item The cohort waits until the expected transaction vote timeout time and gets the voting decision from the blockchain through \texttt{GetVotingDecision()}.
  \item If the voting decision is to commit the transaction, the cohort commits the sub-transaction onto the database and releases any acquired locks; otherwise, it aborts the sub-transaction in the database and releases any acquired locks.
  \item (Independent of the previous steps) The client waits until the vote timeout time and requests the transaction result from the coordinator through \texttt{GetTransactionResult()}, using the transaction ID given in step 1.
  \item The coordinator gets (1) the voting decision of the inquiry transaction from the blockchain through \texttt{GetTransactionResult()} and (2) the \texttt{Get} operation results from each cohort.
\end{enumerate}

@@

\section{Implementation}
In this section we first describe the implementation of our overall system. Then, we illustrate the implementation of individual components. The source code of our implementation is available at \cite{our_code} licensed under GNU Lesser General Public License \cite{lgpl}. Our implementation depends on the following libraries: truffle \cite{github_truffle}, ganache \cite{github_ganache}, sqlite3 \cite{github_sqlite3}, grpc \cite{github_grpc}, web3 \cite{github_web3}, abseil-cpp \cite{github_absl}, rule\_nodejs \cite{github_rulejs}, gflags \cite{github_gflags}, glog \cite{github_glog}, openssl \cite{github_openssl}, threadpool \cite{Shoshany2021_ThreadPool}, lmdb \cite{github_lmdb}, and lmdbxx \cite{github_lmdbxx}.

@@

@@

  \begin{table}[hbtp]
    \centering
    \caption{Gas used, cost in ETH/USD per blockchain transaction for a successful 2PC commit with 2 cohorts. Data as of 2022/05/30.}
    \label{table:cost}
    \begin{tabular}{|p{1.8cm}|p{1.8cm}|p{2cm}|p{1.5cm}|}
      \hline
          & Gas Used (Gwei) &  Cost in ETH & Cost in USD \\
          \hline
      StartVoting &73441 &0.000073441 & 0.143\\
      \hline
      Vote 1 &56451	&0.000056451 &0.110\\
      \hline
      Vote 2 &39513 &0.000039513 &0.077\\
      \hline
      Total &169405 &0.000169405 &0.330\\
      \hline
    \end{tabular}
  \end{table}
